Do motif roles provide unique information about species risk of extinction?

### 2021-06-29 manuscript/motifs_vs_degree.tex
Updates from Overleaf

        \begin{figure}
            \centering
            \includegraphics[height=.5\textheight]{figures/persistence_motif_profiles.eps}
            \caption{The proportions of the four motifs in a network's motif profile are related to the mean persistence of species in the network. Specifically, persistence decreases as the proportion of omnivory in the network's motif profile increases while persistence increases with the proportions of the other three motifs. This was true for all levels of disturbance to basal resources; the interactions between motif profiles and disturbance were significant but small. Relationships are shown for the observed range of proportions for each motif.}      
            \label{fig:motif_profile_persistence}
        \end{figure}

>>>>

        \begin{figure}
            \centering
            \includegraphics[height=.5\textheight]{figures/persistence_motif_profiles.eps}
            \caption{The proportions of the four motifs in a network's motif profile are related to the mean persistence of species in the network. Specifically, persistence decreases as the proportion of omnivory in the network's motif profile increases while persistence increases with the proportions of the other three motifs. Interactions between motif profiles and disturbance were significant but small. Here we show the relationships of probabilities of extinction of basal resources of 0.1 (top set of lines) and 0.5 (bottom set of lines). Relationships are shown for the observed range of proportions for each motif.}      
            \label{fig:motif_profile_persistence}
        \end{figure}
